Descriptive analysis

### 2021-03-23 README.Rmd
Depackagify

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

@@

In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2021"
```

@@

In order to reproduce this project, you'll need to install ASDF:

### 2021-03-23 analysis/01_get-merge-data.Rmd
Depackagify

---
title: "Process and merge data"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.retina = 2,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 100))  # For output

library(tidyverse)
library(canaryNGOs)
library(readxl)
library(haven)
library(countrycode)
library(states)
library(WDI)
library(lubridate)
library(DT)
library(naniar)
library(scales)
library(here)

>>>>

---
title: "Process and merge data"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
editor_options: 
  chunk_output_type: console
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 100))  # For output

library(tidyverse)
library(readxl)
library(haven)
library(countrycode)
library(states)
library(WDI)
library(lubridate)
library(DT)
library(naniar)
library(scales)
library(here)

### 2021-03-23 analysis/02_descriptive-analysis.Rmd
Depackagify

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(canaryNGOs)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)

>>>>

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)
